Design-based estimates for N2O from the NLA 2017 Survey

### 2025-03-06 manuscript/manuscript_file.Rmd
Edits made in DMAP repo required to knit manuscript

# list of file paths for objects saved
f <- list()
for(i in 1:N){
    f[i] <- paste0("/manuscript/manuscript_files/",
    objs[i], ".rda")
    }

# load files if they exist
for(i in 1:N){
  if(file.exists(f[[i]]))
    load(f[[i]])
  else
  # source scripts------
  # some libraries are called within this script.  Not sure if that is necessary
  # if libraries are also called above.  Thus far I'm including necessary
  # library calls in external script.
  # see above for .Rmd working directory
    source("manuscript/manuscript_support.R", local = knitr::knit_global())
}

@@

# list of file paths for objects saved
f <- list()
for(i in 1:N){
    f[i] <- paste0("/manuscript/manuscript_figures/",
    objs[i])
    }

>>>>

# list of file paths for objects saved
f <- list()
for(i in 1:N){
    f[i] <- paste0("./manuscript/manuscript_files/",
    objs[i], ".rda")
    }

# load files if they exist
for(i in 1:N){
  if(file.exists(f[[i]]))
    load(f[[i]])
  else
  # source scripts------
  # some libraries are called within this script.  Not sure if that is necessary
  # if libraries are also called above.  Thus far I'm including necessary
  # library calls in external script.
  # see above for .Rmd working directory
    source("./manuscript/manuscript_support.R", local = knitr::knit_global())
}

@@

# list of file paths for objects saved
f <- list()
for(i in 1:N){
    f[i] <- paste0("./manuscript/manuscript_figures/",
    objs[i])
    }

### 2025-03-06 scripts/DG_sensitivity_to_measurement_error.Rmd
Edits made in DMAP repo required to knit manuscript

```{r plot_map_ratio_all_air, echo=FALSE, fig.align='center', fig.width=8, fig.asp=0.6}
## load ecoregions----
# read in ecoregion polygons
ecoR <- st_read(dsn = paste0(localPath, 
                             "/Environmental Protection Agency (EPA)/",
                             "ORD NLA17 Dissolved Gas - Documents/inputData"),
                layer = "aggr_ecoregions_simple",
                quiet = TRUE)

>>>>

```{r plot_map_ratio_all_air, echo=FALSE, fig.align='center', fig.width=8, fig.asp=0.6}
## load ecoregions----
# read in ecoregion polygons
ecoR <- st_read("/vsizip/./../inputData/aggr_ecoregions_simple.zip", quiet = TRUE)

### 2025-03-06 scripts/Design_Based_Estimates_N2O.Rmd
Edits made in DMAP repo required to knit manuscript

```{r save_to_drive_1, eval=FALSE, include=TRUE}
write.csv(mean_dissolved, file = "./../inputData/populationEstimates/Survey_Ests_N20_dissolved.csv")
```

@@

```{r save_to_drive_2, eval=FALSE, include=TRUE}
write.csv(mean_sat_ratio, file = "./../inputData/populationEstimates/Survey_Ests_N20_sat.csv")
```

>>>>

```{r save_to_drive_1, eval=TRUE, include=TRUE}
write.csv(mean_dissolved, file = "./../inputData/populationEstimates/Survey_Ests_N20_dissolved.csv")
```

@@

```{r save_to_drive_2, eval=TRUE, include=TRUE}
write.csv(mean_sat_ratio, file = "./../inputData/populationEstimates/Survey_Ests_N20_sat.csv")
```
